---
title: "Simulation Analysis"
format: html
---

First, we load the data from our simulation and clean it.
```{r, message=FALSE}
library(tidyverse)
library(tidytext)

df <- read_csv("combined_sim_res.csv")

df_clean <- df %>% 
  mutate(divergent_transitions = str_extract(warnings, "There were (\\d+)",
                                             group = TRUE) %>% as.numeric(),
         ESS_issue = str_detect(warnings, "ESS"),
         r_hat_issue = str_detect(warnings, "R-hat")) %>% 
  replace_na(list(divergent_transitions = 0, ESS_issue = FALSE,
                  r_hat_issue = FALSE)) %>% 
  filter(term == "intervention")

true_eff_small <- .044
true_eff_large <- .089
```

We check the simulations for potential warnings.

```{r}
n_warnings <- df_clean %>% 
  filter(!is.na(warnings)) %>% 
  nrow()

stopifnot(identical(n_warnings, 0L))
```

Success, we have no warnings, divergent transitions or other issues that might
impair our estimation.

# Small effect
We first explore the outcomes for the small effect.

```{r fig.width=8, fig.height=6}
pdata <- df_clean %>% 
  filter(round(true_effect, 1) == 0, n %in% seq(100, 600, by = 100))

pdata %>% 
  ggplot(aes(x = estimate, y = reorder_within(as.factor(run_id), estimate, n))) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_vline(xintercept = true_eff_small, colour = "red3") +
  geom_vline(xintercept = 0, linetype = 2) +
  scale_y_reordered() +
  theme_minimal() +
  facet_wrap(vars(n), scales = "free_y")
```
We display marginal effects on the probability scale (median estimate of the
posterior) with the respective 95% credibility-intervals.

We clearly see that as the sample size increases, our estimates become less 
variable in terms of credibility intervals.

We further check some numbers.

```{r}
# check for bias and power
df_clean %>% 
  filter(round(true_effect, 1) == 0) %>% 
  group_by(n) %>% 
  summarise(med_eff = median(estimate),
            power = sum(conf.low > 0) / 100,
            median_interval_width = median(conf.high - conf.low)) %>% 
  knitr::kable()
```

From the table, we can make a couple of conclusions:

1. The median effect size across 100 runs per sample size is slightly lower than
the true value for smaller sample sizes. This is expected and desirable, with
the prior expecting an effect size of zero having a larger impact on the final
estimates for small effect sizes.
2. We further compute the power, by calculating the proportion of runs 
where the credibility interval does not include 0. With a sample size
of 400-500, we reach a power of about 75%. The power increases to 90% and above
for larger effect sizes.
3. The credibility intervals get narrower for higher sample sizes. With a sample
size of 500, the credibility interval covers a range of 6.3 percentage points,
with a median estimate of a 4.1% higher rate of data sharing in the intervention
group.

Overall, a sample size of 300 or higher seems to provide reasonable precision
and power, even for such a small effect.


# Larger effect
```{r}
pdata <- df_clean %>% 
  filter(round(true_effect, 1) == 0.1, n %in% seq(100, 600, by = 100))

pdata %>% 
  ggplot(aes(x = estimate, y = reorder_within(as.factor(run_id), estimate, n))) +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_vline(xintercept = true_eff_large, colour = "red3") +
  geom_vline(xintercept = 0, linetype = 2) +
  scale_y_reordered() +
  theme_minimal() +
  facet_wrap(vars(n), scales = "free_y")
```


```{r}
# check for bias and power
df_clean %>% 
  filter(round(true_effect, 1) == .1) %>% 
  group_by(n) %>% 
  summarise(med_eff = median(estimate),
            power = sum(conf.low > 0) / 100,
            median_interval_width = median(conf.high - conf.low)) %>% 
  knitr::kable()

```

Compared to the case of a small expected effect size, a smaller sample size is
necessary to achieve high power in the case of the moderate effect size. With
$n = 300$, we achieve 94% power, which increases further to 100% with larger
samples. Notably, the variability of the estimates is higher than in the case 
with a small effect.
